\hypertarget{course-schedule}{%
\section{Course Schedule}\label{course-schedule}}

\textbf{Subject To Change}. All changes will be announced through email
and on the \href{https://lms.cofc.edu}{OAKS} course page.

\vspace{0.10in}

\noindent \textbf{All readings listed under \emph{Readings} below are
required}. For some weeks I have provided supplemental materials. These
are not required but are strongly encouraged. Apart from the books,
additional readings will also be made available on
\href{https://lms.cofc.edu}{OAKS} or as external links. Readings can be
found under Readings for each module. I recommend doing the readings in
the order listed below and on the module guide.

\hypertarget{books}{%
\subsubsection{Books}\label{books}}

\faBook \hspace{0.005in} \textbf{Birkland}: Birkland, Thomas A. 2020.
\emph{An Introduction to the Policy Process: Theories, Concepts, and
Models of Public Policy Making}. Routledge. 5th Edition

\vspace{0.10in}

\noindent \faBook \hspace{0.005in} \textbf{WS}: Weible, Christopher and
Paul Sabatier (eds). 2018. \emph{Theories of the Policy Process}.
Westview Press. 4th Edition.

\vspace{0.10in}

\noindent \faBook \hspace{0.005in} \textbf{BP}: Bardach, Eugene and Eric
M. Patashnik. 2020. \emph{A Practical Guide for Policy Analysis: The
Eightfold Path to More Effective Problem Solving}. SAGE Press. 6th
Edition.

\vspace{0.10in}

\noindent \faBook \hspace{0.005in} \emph{Other book chapters will be
available as pdfs on} \href{https://lms.cofc.edu}{OAKS}

\hypertarget{articles}{%
\subsubsection{Articles}\label{articles}}

\faFileTextO \hspace{0.005in} You will be reading several peer-reviewed
academic journal articles. \emph{These will be made available as pdfs
on} \href{https://lms.cofc.edu}{OAKS}. In addition, you will be required
to find several journal articles on your own.

\hypertarget{blog-posts}{%
\subsubsection{Blog Posts}\label{blog-posts}}

\faExternalLink \hspace{0.005in} I also provide several links to Paul
\textbf{Cairney}'s excellent series of blog posts,
\href{https://paulcairney.wordpress.com/500-words/}{policy in 500 words}
and \href{https://paulcairney.wordpress.com/1000-words/}{policy in 1000
words}. The blog posts are required reading and should be discussed in
your policy process papers. Professor Cairney's
\href{https://paulcairney.wordpress.com/}{website} also provides
podcasts and a host of other resources that I recommend.

\hypertarget{supplemental-materials}{%
\subsubsection{Supplemental Materials}\label{supplemental-materials}}

\faYoutube \hspace{0.005in} When possible, I have included links to
videos and other materials to supplement the readings.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\SetDate[23/08/2021]

\hypertarget{part-i-foundations}{%
\subsection{Part I: Foundations}\label{part-i-foundations}}

\week \textbf{Introduction and Course Overview}

\begin{itemize}

\item
  \emph{Readings (skim after class)}:

  \begin{itemize}
  
  \item
    \textbf{Birkland}, Chap 1, \emph{Introducing the Policy Process}
  \item
    \textbf{Cairney blog post}
    \href{https://paulcairney.wordpress.com/2016/04/28/policy-in-500-words-what-is-public-policy-and-why-does-it-matter/}{What
    is Public Policy and Why Does it Matter?}
  \item
    \textbf{Cairney blog post}
    \href{https://paulcairney.wordpress.com/2015/10/29/12-things-to-know-about-studying-public-policy/}{12
    Things to Know about Studying Public Policy}
  \end{itemize}
\end{itemize}

\week \textbf{Democracy and the Policy Sciences}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Dahl, Robert A., Chap 4, \emph{What is Democracy?}
  \item
    Dahl, Robert A., Chap 5, \emph{Why Democracy?}
  \item
    Levitsky and Ziblatt, Chapter 1: \emph{How Democracies Die:
    Introduction}
  \item
    \textbf{SKIM}: Smith and Larimer, Chap 1 \emph{Public Policy as a
    Concept and a Field (or Fields) of Study} (\textbf{pgs. 7-15})
  \item
    \textbf{SKIM}: deLeon, Peter. 1995. ``Democratic Values and the
    Policy Sciences.'' \emph{American Journal of Political Science}
    39(4): 886--905.
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in} \href{https://youtu.be/EdB1zr1GplA}{How
    Democracies Die - Interview with Harvard Professor Steven Levitsky}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 1}
  \end{itemize}
\end{itemize}

\week \textbf{Equality and Social Constructions}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Dahl, Robert A., Chap 6, \emph{Why Political Equality I? Intrinsic
    Equality}
  \item
    Dahl, Robert A., Chap 7, \emph{Why Political Equality II? Civic
    Competence}
  \item
    powell, john a., Chap 1, \emph{Post-Racialism or Targeted
    Universalism?}
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2016/01/08/policy-concepts-in-1000-words-the-social-construction-of-target-populations/}{The
    Social Construction of Target Populations}
  \item
    \textbf{SKIM}: Schneider, Ingram, and deLeon, \emph{Democratic
    Policy Design: Social Construction of Target Populations}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in}
    \href{https://youtu.be/a0At2xbQB7w}{Targeted Universalism}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 2}
  \end{itemize}
\end{itemize}

\week \textbf{The Policymaking Process}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Birkland}, Chap 2, \emph{Elements of the Policy Making
    System} (\textbf{pages 32-37, skim the rest})
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2013/11/11/policy-concepts-in-1000-words-the-policy-cycle-and-its-stages/}{The
    Policy Cycle and its Stages}
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2017/07/11/policy-concepts-in-1000-words-the-policy-process/}{The
    Policy Process}
  \item
    Dye, Thomas R. 2013. Chap 1, \emph{Models of Politics: Some Help in
    Thinking About Public Policy}
  \item
    \textbf{Birkland} Chap 3, \emph{The Contexts of Public Policy
    Making}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \textbf{Finding Sustainability podcast},
    \href{https://findsustpod.podbean.com/e/044-policy-processes-and-advocacy-coalitions-with-chris-weible/}{Policy
    processes and advocacy coalitions with Chris Weible}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 3}
  \item
    \textbf{Policy report part 1 draft due}
  \end{itemize}
\end{itemize}

\week \textbf{Institutions, Actors, and Subsystems}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Dahl, Robert A., Chap 8, \emph{What Political Institutions Does
    Large-Scale Democracy Require?}
  \item
    \textbf{Cairney blog post}
    \href{https://paulcairney.wordpress.com/2014/03/28/policy-concepts-in-1000-words-institutions-and-new-institutionalism/}{Institutions
    and New Institutionalism}
  \item
    \textbf{Birkland}, Chap 4, \emph{Official Actors and Their Roles in
    Public Policy}
  \item
    \textbf{Birkland}, Chap 5, \emph{Unofficial Actors and Their Roles
    in Public Policy}
  \item
    \textbf{Cairney blog post}
    \href{https://paulcairney.wordpress.com/2014/03/25/policy-concepts-in-1000-words-networks-sub-government-and-communities/}{Networks,
    Sub-government, and Communities}
  \item
    Anderson, James A., \emph{Levels of Politics}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 4 due}
  \item
    \textbf{Policy report part 2 draft due}
  \end{itemize}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{part-ii-theories-of-the-policy-process}{%
\subsection{Part II: Theories of the Policy
Process}\label{part-ii-theories-of-the-policy-process}}

\week \textbf{Agenda Setting and the Multiple Streams Approach}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Birkland} Chap 6, \emph{Agenda Setting, Power, and Interest
    Groups}
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2013/10/31/policy-concepts-in-1000-words-multiple-streams-analysis/}{Multiple
    Streams Analysis}
  \item
    \textbf{WS} Chap 1: Herweg, et al., \emph{The Multiple Streams
    Framework}
  \item
    \faFileTextO \hspace{0.005in} \emph{Find a peer-reviewed journal
    article on agenda setting and/or the Multiple Streams Approach and
    post it to the discussion on} \href{https://lms.cofc.edu}{OAKS}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \textbf{Video with Prof.~Nikolaos Zahariadis}
    \href{https://www.youtube.com/watch?v=JUlvyBVoJiI}{Multiple Streams
    Approach: An Introduction}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 5 due}
  \end{itemize}
\end{itemize}

\week \textbf{Punctuated Equilibrium}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2013/10/29/policy-concepts-in-1000-words-punctuated-equilibrium-theory/}{Punctuated
    Equilibrium Theory}
  \item
    \textbf{WS} Chap 2: Baumgartner, Jones, and Mortensen,
    \emph{Punctuated Equilibrium Theory: Explaining Stability and Change
    in Public Policymaking}.
  \item
    \emph{Find a peer-reviewed journal article using Punctuated
    Equilibrium Theory (PET)}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in} \textbf{Video with Prof.~Frank
    Baumgartner}
    \href{https://www.youtube.com/watch?v=jX2ecS7ri2I}{Punctuated
    Equilibrium: An Introduction}
  \item
    \faYoutube \hspace{0.005in} \textbf{Video with Prof.~Frank
    Baumgartner}
    \href{https://www.youtube.com/watch?v=jX2ecS7ri2I}{Punctuated
    Equilibrium: Applications}
  \item
    \href{https://www.comparativeagendas.net/}{Comparative Policy
    Agendas website}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 6 due}
  \end{itemize}
\end{itemize}

\week \textbf{Fall Break}

\week \textbf{Advocacy Coalition Framework}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2013/10/30/policy-concepts-in-1000-words-the-advocacy-coalition-framework/}{The
    Advocacy Coalition Framework}
  \item
    \textbf{WS} Chap 4: Jenkins-Smith, Nohrstedt, Weible, and Ingold,
    \emph{The Advocacy Coalition Framework: An Overview of the Research
    Program}
  \item
    Weible, Christopher M, and Karin Ingold. 2018. ``Why Advocacy
    Coalitions Matter and Practical Insights About Them.'' \emph{Policy
    \& Politics} 46(2): 325--43.
  \item
    \emph{Find a peer-reviewed journal article using the Advocacy
    Coalition Framework (ACF)}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in} \textbf{Video with Prof.~Christopher
    Weible} \href{https://www.youtube.com/watch?v=-IXuncwc_kE}{Weible On
    ACF}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{‌Reflection paper 7 due}
  \end{itemize}
\end{itemize}

\week \textbf{Narrative Policy Framework}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2015/03/06/policy-concepts-in-1000-words-critical-policy-studies-and-the-narrative-policy-framework/}{Critical
    Policy Studies and the Narrative Policy Framework}
  \item
    \textbf{WS} Chap 5: Shanahan, Jones, McBeth, Radaelli, \emph{The
    Narrative Policy Framework}
  \item
    Crow, Deserai, and Michael Jones. 2018. ``Narratives as Tools for
    Influencing Policy Change.'' \emph{Policy \& Politics} 46(2):
    217--34.
  \item
    \emph{Find a peer-reviewed journal article using the Narrative
    Policy Framework (NPF)}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \href{https://www.narrativepolicyframework.org/}{Narrative Policy
    Framework website}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{‌Reflection paper 8 due}
  \end{itemize}
\end{itemize}

\week \textbf{The Institutional Analysis and Development Framework and Social-Ecological Systems}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2019/02/03/policy-concepts-in-1000-words-the-institutional-analysis-and-development-framework-iad-and-governing-the-commons/}{The
    Institutional Analysis and Development Framework (IAD) and Governing
    the Commons}
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2019/02/03/policy-in-500-words-the-social-ecological-systems-framework/}{The
    Social-Ecological Systems Framework}
  \item
    \textbf{WS} Chap 6: Schlager and Cox, \emph{The IAD Framework and
    SES Framework: An Introduction and Assessment of the Ostrom Workshop
    Frameworks}
  \item
    \emph{Find a peer-reviewed journal article using the IAD OR the SES
    framework}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in} \textbf{Video with Dr.~Elinor Ostrom}
    \href{https://www.youtube.com/watch?v=D1xwV2UDPAg}{Elinor Ostrom on
    managing ``common pool'' resources}
  \item
    McGinnis, Michael D. 2011. ``An Introduction to IAD and the Language
    of the Ostrom Workshop: A Simple Guide to a Complex Framework.''
    \emph{Policy Studies Journal} 39(1): 169--83.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{‌Reflection paper 9 due}
  \end{itemize}
\end{itemize}

\week \textbf{Applying the Theories of the Policy Process}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    Weible, Christopher M., Tanya Heikkila, Peter deLeon, and Paul A.
    Sabatier. 2012. ``Understanding and Influencing the Policy
    Process.'' \emph{Policy Sciences} 45(1): 1--21.
  \item
    Cairney, Paul. 2015. ``How Can Policy Theory Have an Impact on
    Policymaking? The Role of Theory-Led Academic--Practitioner
    Discussions.'' \emph{Teaching Public Administration} 33(1): 22--39.
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{‌Reflection paper 10 due}
  \item
    \textbf{Be prepared to discuss your policy report}
  \end{itemize}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{part-iii-applied-policy-research}{%
\subsection{Part III: Applied Policy
Research}\label{part-iii-applied-policy-research}}

\week \textbf{Policy Design and Implementation}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Birkland} Chap 9, \emph{Policy Design and Policy Tools}
  \item
    \textbf{SKIM}: \textbf{BP} Appendix B: Things Governments Do
  \item
    \textbf{Birkland} Chap 10, \emph{Policy Implementation, Failure, and
    Learning} (\textbf{pgs. 342-353})
  \item
    Herd and Monynihan Chap 1, \emph{Administrative Burdens:
    Introduction}
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \faYoutube \hspace{0.005in}
    \href{https://youtu.be/Y4VqvfcRTec}{Administrative Burden:
    Policymaking by Other Means: Professor Don Moynihan (2019)}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 11}
  \item
    \textbf{Policy report part 3 due}
  \end{itemize}
\end{itemize}

\week \textbf{Policy Analysis and Evaluation}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Birkland} Chap 8, \emph{Decision-Making and Policy Analysis}
  \item
    Radin, Beryl A., Chap 6, \emph{The Tools of the Trade}
  \item
    \textbf{Cairney blog post}:
    \href{https://paulcairney.wordpress.com/2013/12/21/policy-concepts-in-1000-words-success-and-failure-evaluation/}{Success
    and Failure (Evaluation)}
  \item
    deLeon, Peter. 1992. ``The Democratization of the Policy Sciences.''
    \emph{Public Administration Review} 52(2): 125--29.
  \end{itemize}
\item
  \emph{Supplemental Materials}:

  \begin{itemize}
  
  \item
    \href{https://www.brookings.edu/blog/brown-center-chalkboard/2019/06/14/does-head-start-work-the-debate-over-the-head-start-impact-study-explained/?utm_campaign=Brookings\%20Brief\&utm_source=hs_email\&utm_medium=email\&utm_content=73766212}{Does
    Head Start work? The debate over the Head Start Impact Study,
    explained}
  \item
    \href{https://www.sac.usace.army.mil/Missions/Civil-Works/Supplemental-Funding/Charleston-Peninsula-Study/}{Army
    Corp of Engineers Charleston Peninsula Study}
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Reflection paper 12}
  \item
    \textbf{Policy report part 4 due}
  \end{itemize}
\end{itemize}

\week \textbf{Doing Policy Analysis}

\begin{itemize}

\item
  \emph{Readings}:

  \begin{itemize}
  
  \item
    \textbf{Cairney blog post}
    \href{https://paulcairney.wordpress.com/2018/10/25/evidence-based-policymaking-and-the-new-policy-sciences-2/}{Evidence-based
    policymaking and the `new policy sciences'}
  \item
    \textbf{BP}: Parts I-IV
  \end{itemize}
\item
  \emph{Assignments}:

  \begin{itemize}
  
  \item
    \textbf{Course reflection paper due}
  \end{itemize}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Policy report DUE Friday, December 10 by 11:59 PM}

\textbf{Decision memo DUE Friday, December 10 by 11:59 PM}
